Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-11-30 paperIEEE.tex
Start discussion
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@68 db7c848b-7755-4df2-b763-8796797afa52

>>>>

We have presented a significantly improved generic parallel rendering system
over the original publication \cite{EMP:09}. While the original publication
motivated the system design, this publication describes a feature-rich, mature
implementation capable of supporting a wide variety of use cases. We doubled the
support for scalable rendering modes, many of which presented for the first
time. We present new runtime adaptations for better load balance and
performance, describe how common optimizations are integrated into the system,
making Equalizer the most generically available scalable rendering system.

Furthermore, we present many new features needed in parallel rendering
applications, from advanced Virtual Reality support to advanced display system
setup for 2D/3D integration, auto-configuration and runtime reconfiguration, and
an advanced network data synchronization library tailored to parallel rendering
applications. We highlight a few commercial and research applications
underlining the generic and versatile system implemenation.
